### 2022-06-28 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@bfb6721e341ce678ea9848f21ba6695a41b0571f 🚀

The greatest evolutionary potential for zoonotic emergence exists where
pathogen pools have a high genetic diversity and high propensity for
cross-species transmission. In our framework, emergence risk is
therefore maximized under higher phylogenetic diversity (viruses are
exposes to different host clades), higher host uniqueness (viruses are
experiencing novel, heterogeneous host traits combinations), and low to
medium viral sharing (host-virus pairs can coevolve independently, but
divergent viruses may still have opportunities for recombination). In
fig.~\ref{fig:trivariate}, this corresponds to yellow areas (dynamics
dominated by low viral sharing, with equal contributions of selection
mosaics and trait remixing; southeast Asia, and the Indian
sub-continent), green-yellow areas (dynamics with low viral sharing but
dominated by the selection mosaic effect of host diversity; Africa below
the Sahara desert), and red-yellow areas (dynamics with low viral
sharing but dominated by trait remixing in host communities; the Middle
East). Translating this axis of variation back into a univariate risk
map (fig.~\ref{fig:risk}) highlights that this evolutionary landscape
has a striking correspondence to regions where zoonotic
betacoronaviruses have previously emerged.

>>>>

The greatest evolutionary potential for zoonotic emergence exists where
pathogen pools have a high genetic diversity and high propensity for
cross-species transmission. In our framework, emergence risk is
therefore maximized under higher phylogenetic diversity (viruses are
exposes to different host clades), higher host uniqueness (viruses are
experiencing novel, heterogeneous host traits combinations), and low to
medium viral sharing (host-virus pairs can coevolve independently, but
divergent viruses may still have opportunities for recombination). In
fig.~\ref{fig:trivariate}, this corresponds to yellow areas (dynamics
dominated by low viral sharing, with equal contributions of selection
mosaics and trait remixing; southeast Asia, and the Indian
sub-continent), green-yellow areas (dynamics with low viral sharing but
dominated by the selection mosaic effect of host diversity; sub-Saharan
Africa), and red-yellow areas (dynamics with low viral sharing but
dominated by trait remixing in host communities; the Middle East).
Translating this axis of variation back into a univariate risk map
(fig.~\ref{fig:risk}) highlights that this evolutionary landscape has a
striking correspondence to regions where zoonotic betacoronaviruses have
previously emerged.
